### 2016-09-29 outline.rmd
I went shopping ...

The shift from a handwritten list to 'Have you forgotten?' is perhaps a development in memory practices. It reminds me of the game 'I went shopping and I bought ... ' that I play with children sometimes at the dinner table to settle them down. The game is about remembering a well-ordered list of items - a is apple, b is for banana, c is for carrot.  The point of the game is to use the well-ordered set of labels provided by the sequence of letters in the alphabet to remember a random and perhaps very diverse list of items. The longer the game continues, the harder it is to remember since the shopping list grows longer. At the same time, the many repetitions of this list, the fact that each player recites the whole list, helps memorisation. One trick in playing this game is to choose items that are quite unexpected. Rather than `ham`, list `halva`; rather than `fish`, add `face cream.` This is especially useful for adults in beating children. The children have better memories for items they know, but adults know more unexpected items.

Something similar applies to recommendation systems. The system can remember very many things.
It may know everything you bought in the last few years on that site, and it can easily see what you would normally buy and add those as suggestions.
But a recommendation system finds it much harder to suggest items that you have not forgotten but may have never bought. If you do buy recommended items, then the recommender system has been effective. It has led to a 'conversion.'

>>>>

The shift from a handwritten list to 'Have you forgotten?' is perhaps a **development in memory practices.** It reminds me of the game 'I went shopping and I bought ... ' that I play with children sometimes at the dinner table to settle them down. The game is about remembering a well-ordered list of items - a is apple, b is for banana, c is for carrot.  The point of the game is to use the well-ordered set of labels provided by the sequence of letters in the alphabet to remember a random and perhaps very diverse list of items. The longer the game continues, the harder it is to remember since the shopping list grows longer. At the same time, the many repetitions of this list, the fact that each player recites the whole list, helps memorisation. One trick in playing this game is to choose items that are quite unexpected or increasingly random. Rather than `ham`, list `halva`; rather than `fish`, add `face cream.` This is especially useful for adults in beating children. The children have better memories for items they know, but adults know more unexpected items. On the other hand, very unexpected items are quite easy to remember and tend to even the score in the favour of the children. Balancing between the improbable and memorable ...

Something similar applies to recommendation systems. The system can remember very many things.
It may know everything you bought in the last few years on that site, and it can easily see what you would normally buy and add those as suggestions.
But a recommendation system finds it much harder to suggest items that you have not forgotten but may have never bought. If you do buy recommended items, then the recommender system has been effective. It has led to a **'conversion.'** From a supermarket perspective, the conversion should be high-value.
